Pillar 2 - Topic Modeling

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
section added for presentation

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
####stopwords for keywords
THIS NEEDS CLEANING!!!!!!!!!!!!!!!!!!!!!!!!!
```{r}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

>>>>

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")
